Check Coverage

### 2019-08-26 analysis/merge_data.Rmd

fd_data <- biotime_traits %>% 
  filter(study_id == 56) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd(.x, study = .y$study_id, plot = .y$plot))
```

>>>>

fd_data <- biotime_traits %>% 
  filter(!is.na(-plot)) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))
```

Read data back in:
```{r}
fd_data <- dir(here::here("data", "fd_output"), "*.tsv") %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(read_tsv)
```
